Psychological Needs During Intergroup Contact

### 2021-12-15 Methods-and-Results.Rmd
robust tbl started

# divide into trait and state
dtWorkerSupp$workerWithinBetween <-
  MlTraitState(
    data = dtWorkerSupp$workerInteractionType,
    id = "PID",
    selection =
      c(
        "keyMotiveFulfilled",
        "competence.daily.all",
        "autonomy.daily.all",
        "relatedness.daily.all",
        "thermometerDutch_1",
        "keymotive_fulfillemt_1",
        "competence_1",
        "autonomy_1",
        "relatedness_1", 
        "quality_overall_1"
      )
  )

@@

```{r WorkerFreqAttCor, include=FALSE}
# correlation panel
pairs.panels.new(
  dtWorkerSupp$workerAvFreQual %>% select(SumContactNL, SumContactNLAll, AvQuality, AvAttitude),
  labels = c(
    "Sum:\nNumer of beeps with Outgroup Contact (NL)",
    "Sum:\nNumber of Outgroup Contacts (NL)",
    "Mean:\nInteraction Quality",
    "Mean:\nOutgroup Attitudes (NL)"
  )
)

@@

# regression
mdlWorker$lmAttFreqQualX <-
  lm(AvAttitude ~ SumContactNL * AvQuality, data = dtWorkerSupp$workerAvFreQual)
# summary(lmWorkerAttFreqQualX)

summ(
  mdlWorker$lmAttFreqQualX,
  confint = TRUE,
  digits = 3,
  center = TRUE
)

@@

interactions::interact_plot(
  mdlWorker$lmAttFreqQualX,
  pred = AvQuality,
  modx = SumContactNL,
  interval = TRUE,
  partial.residuals = TRUE
)

interactions::johnson_neyman(mdlWorker$lmAttFreqQualX,
                             pred = AvQuality,
                             modx = SumContactNL,
                             alpha = .05)

@@

However, despite the missing relationship with the number of interactions, we find a medium sized correlation between the participants' Average Interaction Quality and their Average Outgroup Attitudes. Thus within our data participants with a higher quality outgroup interactions also held more positive attitudes towards that group. And when considering the number of interactions and average interaction quality jointly in a linear regression, we additionally find a statistically significant interaction term (\textit{b} = `r coef(summary(mdlWorker$lmAttFreqQualX))["SumContactNL:AvQuality","Estimate"] %>% round(2) %>% format(nsmall=2)`, \textit{t}(`r mdlWorker$lmAttFreqQualX$df.residual`) = `r coef(summary(mdlWorker$lmAttFreqQualX))["SumContactNL:AvQuality","t value"] %>% round(2) %>% format(nsmall=2)`, \textit{p} = `r coef(summary(mdlWorker$lmAttFreqQualX))["SumContactNL:AvQuality","Pr(>|t|)"] %>% round(3) %>% format(nsmall=3)`, $\eta_p^2$ = `r mdlWorker$lmAttFreqQualXEta %>% filter(Parameter == "SumContactNL:AvQuality") %>% select(Eta2_partial) %>% as.numeric %>% round(2) %>% format(nsmall=2)`). Looking at a floodlight analysis of the effect, we find that in our sample with an increasing number of interactions the positive effect of average interaction quality becomes weaker. However, it should be noted that this is based on data aggregating all within participant nuances and is only the date of 21 people.

@@

# divide into trait and state
dtStudentSupp$studentWithinBetween <-
  MlTraitState(
    data = dtStudentSupp$studentInteractionType,
    id = "PID",
    selection =
      c(
        "KeyNeedFullfillment",
        "Competence",
        "Autonomy",
        "Relatedness",
        "AttitudesDutch",
        "quality_overall"
      )
  )
dtStudentSupp$studentOutWithinBetween <-
  MlTraitState(
    data = dtStudentSupp$studentInteractionType %>% filter(OutgroupInteraction == "Yes"),
    id = "PID",
    selection =
      c(
        "KeyNeedFullfillment",
        "Competence",
        "Autonomy",
        "Relatedness",
        "AttitudesDutch",
        "quality_overall"
      )
  )
```

@@

# look at frequencies of characteristics 
table(medicalSampleInfo$age)
table(medicalSampleInfo$gender)
table(as.character(medicalSampleInfo$nationality))
```

@@

# OLS 
# Study 1:
mdlWorker$lmAttFreqQualX <-
  lm(AvAttitude ~ SumContactNL * AvQuality, data = dtWorkerSupp$workerAvFreQual)
# Study 2:
mdlStudent$lmAttFreqQualX <-
  lm(AvAttitude ~ SumContactNL_c * AvQuality_c, data = dtStudentSupp$studentContactFreq)
# Study 3: 
mdlMedical$lmAttFreqQualX <-
  lm(AvAttitude ~ SumContactNL_c * AvQuality_c, data = dtMedicalSupp$medicalContactFreq)

@@

mdlTbl$coef <- mapvalues(mdlTbl$coef, 
          from = c("sigmaSq", "tau00", "tau11", "rho01", "rho00"), 
          to = c("\\sigma^2", "\\tau_{00}", "\\tau_{11}", "\\rho_{01}", "\\rho_{00}"))

# Still need to pack rows
mdlTbl %>%
  select(-one_of(coef2)) %>%
  replace(is.na(.), "") %>%
  kbl(
    .,
    caption = "Test",
    #format = "latex",
    linesep = "",
    booktabs = T,
    align = rep("c", ncol(.)),
    escape = FALSE,
    digits = 3
  ) %>%
  kable_classic() %>%
  add_header_above(., mdlTblHeader2) %>%
  add_header_above(., mdlTblHeaderFreq) %>%
  pack_rows("Fixed", 1, 4) %>%
  pack_rows("Random", 5, 9) %>%
  pack_rows("Fit", 10, 21)

@@

>>>>

# divide into trait and state
dtWorkerSupp$workerWithinBetween <-
  MlTraitState(
    data = dtWorkerSupp$workerInteractionType,
    id = "PID",
    selection =
      c(
        "keyMotiveFulfilled",
        "competence.daily.all",
        "autonomy.daily.all",
        "relatedness.daily.all",
        "thermometerDutch_1",
        "keymotive_fulfillemt_1",
        "competence_1",
        "autonomy_1",
        "relatedness_1", 
        "quality_overall_1", 
        "OutgroupInteraction",
        "NonOutgroupInteraction"
      )
  )

@@

```{r WorkerFreqAttCor, include=FALSE}
dtWorkerSupp$workerAvFreQual <-
  dtWorkerSupp$workerAvFreQual %>%
  mutate(
    SumContactNL_c = SumContactNL - mean(SumContactNL, na.rm = TRUE),
    SumContactNLAll_c = SumContactNLAll - mean(SumContactNLAll, na.rm = TRUE),
    AvAttitude_c = AvAttitude - mean(AvAttitude, na.rm = TRUE),
    AvQuality_c = AvQuality - mean(AvQuality, na.rm = TRUE)
  )

# correlation panel
pairs.panels.new(
  dtWorkerSupp$workerAvFreQual %>% select(SumContactNL, SumContactNLAll, AvQuality, AvAttitude),
  labels = c(
    "Sum:\nNumer of beeps with Outgroup Contact (NL)",
    "Sum:\nNumber of Outgroup Contacts (NL)",
    "Mean:\nInteraction Quality",
    "Mean:\nOutgroup Attitudes (NL)"
  )
)

@@

# regression
mdlWorker$lmAttFreqQualX <-
  lm(AvAttitude ~ SumContactNL_c * AvQuality_c, data = dtWorkerSupp$workerAvFreQual)
# summary(lmWorkerAttFreqQualX)

summ(
  mdlWorker$lmAttFreqQualX,
  confint = TRUE,
  digits = 3
)

@@

interactions::interact_plot(
  mdlWorker$lmAttFreqQualX,
  pred = AvQuality_c,
  modx = SumContactNL_c,
  interval = TRUE,
  partial.residuals = TRUE
)

interactions::johnson_neyman(mdlWorker$lmAttFreqQualX,
                             pred = AvQuality_c,
                             modx = SumContactNL_c,
                             alpha = .05)

@@

However, despite the missing relationship with the number of interactions, we find a medium sized correlation between the participants' Average Interaction Quality and their Average Outgroup Attitudes. Thus within our data participants with a higher quality outgroup interactions also held more positive attitudes towards that group. And when considering the number of interactions and average interaction quality jointly in a linear regression, we additionally find a statistically significant interaction term (\textit{b} = `r coef(summary(mdlWorker$lmAttFreqQualX))["SumContactNL_c:AvQuality_c","Estimate"] %>% round(2) %>% format(nsmall=2)`, \textit{t}(`r mdlWorker$lmAttFreqQualX$df.residual`) = `r coef(summary(mdlWorker$lmAttFreqQualX))["SumContactNL_c:AvQuality_c","t value"] %>% round(2) %>% format(nsmall=2)`, \textit{p} = `r coef(summary(mdlWorker$lmAttFreqQualX))["SumContactNL_c:AvQuality_c","Pr(>|t|)"] %>% round(3) %>% format(nsmall=3)`, $\eta_p^2$ = `r mdlWorker$lmAttFreqQualXEta %>% filter(Parameter == "SumContactNL_c:AvQuality_c") %>% select(Eta2_partial) %>% as.numeric %>% round(2) %>% format(nsmall=2)`). Looking at a floodlight analysis of the effect, we find that in our sample with an increasing number of interactions the positive effect of average interaction quality becomes weaker. However, it should be noted that this is based on data aggregating all within participant nuances and is only the date of 21 people.

@@

# divide into trait and state
dtStudentSupp$studentWithinBetween <-
  MlTraitState(
    data = dtStudentSupp$studentInteractionType,
    id = "PID",
    selection =
      c(
        "KeyNeedFullfillment",
        "Competence",
        "Autonomy",
        "Relatedness",
        "AttitudesDutch",
        "quality_overall",
        "OutgroupInteraction",
        "NonOutgroupInteraction"
      )
  )
dtStudentSupp$studentOutWithinBetween <-
  MlTraitState(
    data = dtStudentSupp$studentInteractionType %>% filter(OutgroupInteraction == "Yes"),
    id = "PID",
    selection =
      c(
        "KeyNeedFullfillment",
        "Competence",
        "Autonomy",
        "Relatedness",
        "AttitudesDutch",
        "quality_overall"
      )
  )
```

@@

# look at frequencies of characteristics 
table(medicalSampleInfo$age)
table(medicalSampleInfo$gender)
table(as.character(medicalSampleInfo$nationality))

# divide into trait and state
dtMedicalSupp$medicalWithinBetween <- 
  MlTraitState(
    data = dtMedical$full,
    id = "PID",
    selection =
      c(
        "OutgroupInteraction",
        "NonOutgroupInteraction"
      )
  )
```

@@

# OLS 
# Study 1:
mdlWorker$lmAttFreqQualX <-
  lm(AvAttitude ~ SumContactNL_c * AvQuality_c, data = dtWorkerSupp$workerAvFreQual)
# Study 2:
mdlStudent$lmAttFreqQualX <-
  lm(AvAttitude ~ SumContactNL_c * AvQuality_c, data = dtStudentSupp$studentContactFreq)
# Study 3: 
mdlMedical$lmAttFreqQualX <-
  lm(AvAttitude ~ SumContactNL_c * AvQuality_c, data = dtMedicalSupp$medicalContactFreq)

tabModelTest <- tab_model(mdlWorker$lmAttFreqQualX,
                          mdlStudent$lmAttFreqQualX,
                          mdlMedical$lmAttFreqQualX)

library(XML)
df <- data.frame(readHTMLTable(htmlParse(tabModelTest))[1])
# first row as colnames
colnames(df) <- df[1,]
# remove the fake first row
df <- df[-1,]

# lme
# Study 1: 
dtWorkerSupp$workerWithinBetween$AttitudesDutch <- dtWorkerSupp$workerWithinBetween$thermometerDutch_1
mdlWorker$lmerInterceptAttTypeTbl <- lmer(
    AttitudesDutch ~ OutgroupInteraction + NonOutgroupInteraction + (1 | PID),
    data = dtWorkerSupp$workerWithinBetween
  )
dtWorkerSupp$workerWithinBetween$AttitudesDutch_zwc <- dtWorkerSupp$workerWithinBetween$thermometerDutch_1
mdlWorker$lmerInterceptAttTypeTblZ <- lmer(
    AttitudesDutch_zwc ~ OutgroupInteraction_zwc + NonOutgroupInteraction_zwc + (1 | PID),
    data = dtWorkerSupp$workerWithinBetween
  )
# Study 2:
mdlStudent$lmerSlopesAttType <- lmer(
    AttitudesDutch ~
      OutgroupInteraction + NonOutgroupInteraction +
      (1 + OutgroupInteraction + NonOutgroupInteraction | PID),
    data = dtStudentSupp$studentWithinBetween
  )
mdlStudent$lmerSlopesAttTypeZ <- lmer(
    AttitudesDutch_zwc ~
      OutgroupInteraction_zwc + NonOutgroupInteraction_zwc +
      (1 + OutgroupInteraction_zwc + NonOutgroupInteraction_zwc | PID),
    data = dtStudentSupp$studentWithinBetween
  )
# Study 3:
mdlMedical$lmerSlopesAttType <- lmer(
    AttitudesDutch ~
      OutgroupInteraction + NonOutgroupInteraction +
      (1 + OutgroupInteraction + NonOutgroupInteraction | PID),
    data = dtMedicalSupp$medicalWithinBetween
  )
mdlMedical$lmerSlopesAttTypeZ <- lmer(
    AttitudesDutch_zwc ~
      OutgroupInteraction_zwc + NonOutgroupInteraction_zwc +
      (1 + OutgroupInteraction_zwc + NonOutgroupInteraction_zwc | PID),
    data = dtMedicalSupp$medicalWithinBetween
  )

tab_model(
  mdlWorker$lmerInterceptAttTypeTbl,
  mdlStudent$lmerSlopesAttType,
  mdlMedical$lmerSlopesAttType
)

mdlTblElementsGeneralLmer <- list(
  c(mdlWorker$lmerInterceptAttTypeTbl, mdlWorker$lmerInterceptAttTypeTblZ),
  c(mdlStudent$lmerSlopesAttType, mdlStudent$lmerSlopesAttTypeZ),
  c(mdlMedical$lmerSlopesAttType, mdlMedical$lmerSlopesAttTypeZ)
  )

mdlPrepGeneral <- list()
for (i in 1:length(mdlTblElementsGeneralLmer)) {
  mdlPrepGeneral[[i]] <- lmerTblPrep(mdlTblElementsGeneralLmer[[i]][[1]], mdlTblElementsGeneralLmer[[i]][[2]])
}

mdlTblGeneral <- data.frame(
  coef = c(
    "(Intercept)",
    "OutgroupInteraction",
    "NonOutgroupInteraction",
    names(mdlPrepGeneral[[1]]$random),
    names(mdlPrepGeneral[[1]]$fit)
  )
)
for (i in 1:length(mdlPrepGeneral)){
  mdlTblGeneral <- join(mdlTblGeneral, mdlPrepGeneral[[i]]$mdlTbl, by = "coef")
}

mdlTblHeaderGeneral <- data.frame(
  data = as.character(mdlTblGeneral[mdlTblGeneral$coef == "data",]),
  formula = as.character(mdlTblGeneral[mdlTblGeneral$coef == "formula",])
) %>%
  filter(data != "",
         data != "data") %>%
  mutate(study = str_extract(data, "S1|S2|S3")) %>%
  mutate(study = gsub("S", "Study ", study)) %>%
  mutate(dv = sub(" ~.*", "", formula)) %>%
  mutate(dv = gsub("Raw", " ", dv)) %>%
  mutate(pred = str_extract(formula, "CoreNeed|Allport")) %>%
  mutate(header = paste(study, pred))

mdlTblHeaderGeneralFreq <- rbind.data.frame(rle(mdlTblHeaderGeneral$header)) %>%
  mutate(lengths = lengths*2) %>%
  rename(names = values, span = lengths) %>%
  rbind(c(1, ""), .) %>%
  mutate(span = as.numeric(span)) %>%
  select(names, span)

mdlTblHeaderGeneral2 <- data.frame(names = mdlTblHeaderGeneral$dv, span = 2) %>% 
  mutate(names = as.character(names)) %>%
  rbind(c("", 1), .) %>%
  mutate(span = as.numeric(span))

mdlTblHeaderGeneral2.2 <- rbind.data.frame(rle(mdlTblHeaderGeneral$dv)) %>%
  mutate(lengths = lengths*2) %>%
  rename(names = values, span = lengths) %>%
  rbind(c(1, ""), .) %>%
  mutate(span = as.numeric(span)) %>%
  select(names, span)

mdlTblGeneral$coef <- mapvalues(
  mdlTblGeneral$coef,
  from = c(
    "sigmaSq",
    "tau00",
    "tau11",
    "rho01",
    "rho00",
    "R2_marginal",
    "R2_conditional",
    "R2Marg_R2Cond"
  ),
  to = c(
    "$\\sigma^2$",
    "$\\tau_{00}$",
    "$\\tau_{11}$",
    "$\\rho_{01}$",
    "$\\rho_{00}$",
    "$R^2_{marginal}$",
    "$R^2_{conditional}$",
    "$R^2_{marginal} / R^2_{conditional}$"
  )
)

# Still need to pack rows
mdlTblGeneral %>%
  replace(is.na(.), "") %>%
  kbl(
    .,
    caption = "Intergroup Contact General within PPT.",
    #format = "latex",
    linesep = "",
    booktabs = T,
    align = c("l", rep("c", ncol(.)-1)),
    escape = FALSE,
    digits = 3
  ) %>%
  kable_classic() %>%
  add_header_above(., mdlTblHeaderGeneral2) %>%
  pack_rows("Fixed", 1, 3) %>%
  pack_rows("Random", 4, 8) %>%
  pack_rows("Fit", 9, 21)

@@

mdlTbl$coef <- mapvalues(mdlTbl$coef, 
          from = c("sigmaSq", "tau00", "tau11", "rho01", "rho00", "R2_marginal", "R2_conditional"), 
          to = c("$\\sigma^2$", "$\\tau_{00}$", "$\\tau_{11}$", "$\\rho_{01}$", "$\\rho_{00}$", "$R^2_{marginal}$", "$R^2_{conditional}$"))

# Still need to pack rows
mdlTbl %>%
  replace(is.na(.), "") %>%
  kbl(
    .,
    caption = "Core Need Fulfillment and Allport's Conditions",
    #format = "latex",
    linesep = "",
    booktabs = T,
    align = rep("c", ncol(.)),
    escape = FALSE,
    digits = 3
  ) %>%
  kable_classic() %>%
  add_header_above(., mdlTblHeader2) %>%
  add_header_above(., mdlTblHeaderFreq) %>%
  pack_rows("Fixed", 1, 4) %>%
  pack_rows("Random", 5, 9) %>%
  pack_rows("Fit", 10, 21)

@@

# Full Sample
# Study 1:
robustTblWorkerFull <- 
  dtWorkerSupp$workerWithinBetween %>%
  select(
    AttitudesDutch = thermometerDutch_1,
    AttitudesDutch_zwc = thermometerDutch_1_zwc,
    CoreNeed_cwc = keyMotiveFulfilled_cwc,
    CoreNeed_zwc = keyMotiveFulfilled_zwc,
    OutgroupInteraction = OutgroupInteraction,
    OutgroupInteraction_zwc = OutgroupInteraction_zwc,
    PID = PID
  )
mdlWorkerLmerSlopesAttCoreInt <- lmer(
    AttitudesDutch ~
      CoreNeed_cwc * OutgroupInteraction +
      (1 + CoreNeed_cwc + OutgroupInteraction | PID),
    data = robustTblWorkerFull
  )
mdlWorkerLmerSlopesAttCoreIntZ <- lmer(
    AttitudesDutch_zwc ~
      CoreNeed_zwc * OutgroupInteraction_zwc +
      (1 + CoreNeed_zwc + OutgroupInteraction_zwc | PID),
    data = robustTblWorkerFull
  )
#Study 2:
robustTblStudentFull <- 
  dtStudentSupp$studentWithinBetween %>%
  select(
    AttitudesDutch = AttitudesDutch,
    AttitudesDutch_zwc = AttitudesDutch_zwc,
    CoreNeed_cwc = KeyNeedFullfillment_cwc,
    CoreNeed_zwc = KeyNeedFullfillment_zwc,
    OutgroupInteraction = OutgroupInteraction,
    OutgroupInteraction_zwc = OutgroupInteraction_zwc, 
    PID = PID
  )
mdlStudentLmerSlopesAttCoreInt <- lmer(
    AttitudesDutch ~
      CoreNeed_cwc * OutgroupInteraction +
      (1 + CoreNeed_cwc + OutgroupInteraction | PID),
    data = robustTblStudentFull
  )
mdlStudentLmerSlopesAttCoreIntZ <- lmer(
    AttitudesDutch_zwc ~
      CoreNeed_zwc * OutgroupInteraction_zwc +
      (1 + CoreNeed_zwc + OutgroupInteraction_zwc | PID),
    data = robustTblStudentFull
  )
#Study 3:
robustTblMedicalFull <- 
  dtMedicalSupp$medicalWithinBetween %>%
  select(
    AttitudesDutch = AttitudesDutch,
    AttitudesDutch_zwc = AttitudesDutch_zwc,
    CoreNeed_cwc = KeyNeedFulfillment_cwc,
    CoreNeed_zwc = KeyNeedFulfillment_zwc,
    OutgroupInteraction = OutgroupInteraction,
    OutgroupInteraction_zwc = OutgroupInteraction_zwc, 
    PID = PID
  )
mdlMedicalLmerSlopesAttCoreInt <- lmer(
    AttitudesDutch ~
      CoreNeed_cwc * OutgroupInteraction +
      (1 + CoreNeed_cwc + OutgroupInteraction | PID),
    #data = dtMedical$full
    data = robustTblMedicalFull
  )
mdlMedicalLmerSlopesAttCoreIntZ <- lmer(
    AttitudesDutch_zwc ~
      CoreNeed_zwc * OutgroupInteraction_zwc +
      (1 + CoreNeed_zwc + OutgroupInteraction_zwc | PID),
    #data = dtMedical$full
    data = robustTblMedicalFull
  )

# SDT
# Study 1:
robustTblWorkerOut <- 
  dtWorkerSupp$workerOutWithinBetween %>%
  select(
    AttitudesDutch = thermometerDutch_1,
    AttitudesDutch_zwc = thermometerDutch_1_zwc,
    CoreNeed_cwc = keymotive_fulfillemt_1_cwc,
    CoreNeed_zwc = keymotive_fulfillemt_1_zwc,
    Competence_cwc = competence_1_cwc,
    Competence_zwc = competence_1_zwc,
    Autonomy_cwc = autonomy_1_cwc,
    Autonomy_zwc = autonomy_1_zwc,
    Relatedness_cwc = relatedness_1_cwc,
    Relatedness_zwc = relatedness_1_zwc,
    PID = PID
  )
mdlWorkerOutLmerSlopesCoreSdt <- lmer(
    AttitudesDutch ~
      CoreNeed_cwc + Competence_cwc + Autonomy_cwc + Relatedness_cwc +
      (1 + CoreNeed_cwc + Competence_cwc + Autonomy_cwc + Relatedness_cwc | PID),
    data = robustTblWorkerOut
  )
mdlWorkerOutLmerSlopesCoreSdtZ <- lmer(
    AttitudesDutch_zwc ~
      CoreNeed_zwc + Competence_zwc + Autonomy_zwc + Relatedness_zwc +
      (1 + CoreNeed_zwc + Competence_zwc + Autonomy_zwc + Relatedness_zwc | PID),
    data = robustTblWorkerOut
  )
# Study 2:
robustTblStudentOut <- 
  dtStudentSupp$studentOutWithinBetween %>%
  select(
    AttitudesDutch = AttitudesDutch,
    AttitudesDutch_zwc = AttitudesDutch_zwc,
    CoreNeed_cwc = KeyNeedFullfillment_cwc,
    CoreNeed_zwc = KeyNeedFullfillment_zwc,
    Competence_cwc = Competence_cwc,
    Competence_zwc = Competence_zwc,
    Autonomy_cwc = Autonomy_cwc,
    Autonomy_zwc = Autonomy_zwc,
    Relatedness_cwc = Relatedness_cwc,
    Relatedness_zwc = Relatedness_zwc,
    PID = PID
  )
mdlStudentOutLmerSlopesCoreSdt <- lmer(
    AttitudesDutch ~
      CoreNeed_cwc + Competence_cwc + Autonomy_cwc + Relatedness_cwc +
      (1 + CoreNeed_cwc + Competence_cwc + Autonomy_cwc + Relatedness_cwc | PID),
    data = robustTblStudentOut
  )
mdlStudentOutLmerSlopesCoreSdtZ <- lmer(
    AttitudesDutch_zwc ~
      CoreNeed_zwc + Competence_zwc + Autonomy_zwc + Relatedness_zwc +
      (1 + CoreNeed_zwc + Competence_zwc + Autonomy_zwc + Relatedness_zwc | PID),
    data = robustTblStudentOut
  )
# Study 3:
robustTblMedicalOut <- 
  dtMedicalSupp$medicalOutWithinBetween %>%
  select(
    AttitudesDutch = AttitudesDutch,
    AttitudesDutch_zwc = AttitudesDutch_zwc,
    CoreNeed_cwc = KeyNeedFulfillment_cwc,
    CoreNeed_zwc = KeyNeedFulfillment_zwc,
    Competence_cwc = Competence_cwc,
    Competence_zwc = Competence_zwc,
    Autonomy_cwc = Autonomy_cwc,
    Autonomy_zwc = Autonomy_zwc,
    Relatedness_cwc = Relatedness_cwc,
    Relatedness_zwc = Relatedness_zwc,
    PID = PID
  )
mdlMedicalOutLmerSlopesCoreSdt <- lmer(
    AttitudesDutch ~
      CoreNeed_cwc + Competence_cwc + Autonomy_cwc + Relatedness_cwc +
      (1 + CoreNeed_cwc + Competence_cwc + Autonomy_cwc + Relatedness_cwc | PID),
    data = robustTblMedicalOut
  )
mdlMedicalOutLmerSlopesCoreSdtZ <- lmer(
    AttitudesDutch_zwc ~
      CoreNeed_zwc + Competence_zwc + Autonomy_zwc + Relatedness_zwc +
      (1 + CoreNeed_zwc + Competence_zwc + Autonomy_zwc + Relatedness_zwc | PID),
    data = robustTblMedicalOut
  )

# collect models for table
mdlRobustTblElements <- list(
  # full
  c(mdlWorkerLmerSlopesAttCoreInt, mdlWorkerLmerSlopesAttCoreIntZ),
  c(mdlStudentLmerSlopesAttCoreInt, mdlStudentLmerSlopesAttCoreIntZ),
  c(mdlMedicalLmerSlopesAttCoreInt, mdlMedicalLmerSlopesAttCoreIntZ),
  # outgroup
  c(mdlWorkerOutLmerSlopesCoreSdt, mdlWorkerOutLmerSlopesCoreSdtZ),
  c(mdlStudentOutLmerSlopesCoreSdt, mdlStudentOutLmerSlopesCoreSdtZ),
  c(mdlMedicalOutLmerSlopesCoreSdt, mdlMedicalOutLmerSlopesCoreSdtZ)
  )

mdlRobustPrep <- list()
for (i in 1:length(mdlRobustTblElements)) {
  mdlRobustPrep[[i]] <- lmerTblPrep(mdlRobustTblElements[[i]][[1]], mdlRobustTblElements[[i]][[2]])
}

sapply(mdlRobustPrep, "[[", 1)
sapply(mdlRobustPrep, function(x) x[1]$coeficients$coef)

mdlRobustPrep[[1]]$coeficients$coef

mdlRobustTbl <- data.frame(
  coef = c(
    "(Intercept)",
    "CoreNeed",
    "Quality",
    "Allport",
    names(mdlRobustPrep[[1]]$random),
    names(mdlRobustPrep[[1]]$fit)
  )
)
for (i in 1:length(mdlRobustPrep)){
  mdlRobustTbl <- join(mdlRobustTbl, mdlRobustPrep[[i]]$mdlTbl, by = "coef")
  #mdlTbl <- merge(mdlRobustTbl, mdlRobustPrep[[i]]$mdlTbl, by = "coef", all = TRUE, sort = FALSE, no.dups = TRUE, suffixes=c("", ""))
}

mdlTblHeader <- data.frame(
  data = as.character(mdlRobustTbl[mdlRobustTbl$coef == "data",]),
  formula = as.character(mdlRobustTbl[mdlRobustTbl$coef == "formula",])
) %>%
  filter(data != "",
         data != "data") %>%
  mutate(study = str_extract(data, "S1|S2|S3")) %>%
  mutate(study = gsub("S", "Study ", study)) %>%
  mutate(dv = sub(" ~.*", "", formula)) %>%
  mutate(dv = gsub("Raw", " ", dv)) %>%
  mutate(pred = str_extract(formula, "CoreNeed|Allport")) %>%
  mutate(header = paste(study, pred))

mdlTbl$coef <- mapvalues(mdlTbl$coef, 
          from = c("sigmaSq", "tau00", "tau11", "rho01", "rho00", "R2_marginal", "R2_conditional"), 
          to = c("$\\sigma^2$", "$\\tau_{00}$", "$\\tau_{11}$", "$\\rho_{01}$", "$\\rho_{00}$", "$R^2_{marginal}$", "$R^2_{conditional}$"))

# Still need to pack rows
mdlTbl %>%
  replace(is.na(.), "") %>%
  kbl(
    .,
    caption = "Core Need Fulfillment and Allport's Conditions",
    #format = "latex",
    linesep = "",
    booktabs = T,
    align = rep("c", ncol(.)),
    escape = FALSE,
    digits = 3
  ) %>%
  kable_classic() %>%
  add_header_above(., mdlTblHeader2) %>%
  add_header_above(., mdlTblHeaderFreq) %>%
  pack_rows("Fixed", 1, 4) %>%
  pack_rows("Random", 5, 9) %>%
  pack_rows("Fit", 10, 21)
